Assessment and Optimization of Nowcast Measures for Trend Detection

### 2023-12-15 paper.tex
Update on Overleaf.

\begin{figure}
  \centering
  \includegraphics{plots/simulation_same_rmse_mae/time_series.pdf}
  \caption{Realisation of Simulation~\ref{sec:simulation_rmse_mae} with $T = 100$, $\sigma_y=0.1$, $a = 10$, $p_2 = 0.8$, and $p_3 = (0.8, 0.4)$}
  \label{fig:simulation_rmse_mae_ts}
\end{figure}

\begin{figure}
  \centering
  \begin{subfigure}{.32\textwidth}
  	\includegraphics{plots/simulation_same_rmse_mae/4q_plot_1}
  \end{subfigure}
  \begin{subfigure}{.32\textwidth}
  	\includegraphics{plots/simulation_same_rmse_mae/4q_plot_2}
  \end{subfigure}
    \begin{subfigure}{.32\textwidth}
  	\includegraphics{plots/simulation_same_rmse_mae/4q_plot_3}
  \end{subfigure}
  \caption{4Q-Plot for Simulation~\ref{sec:simulation_rmse_mae} with $T = 100$, $\sigma_y=0.1$, $a = 10$, $p_2 = 0.8$, and $p_3 = (0.8, 0.4)$.}
  \label{fig:simulation_rmse_mae_4q}
\end{figure}

>>>>

\begin{figure}
  \centering
  \includegraphics{plots/simulation_same_rmse_mae/time_series.pdf}
  \caption{Realisation of Simulation~\ref{sec:simulation_rmse_mae} with $T = 100$, $\sigma_y=0.1$, $a = 10$, $p_2 = 0.8$, and $p_3 = (0.9, 0.5)$}
  \label{fig:simulation_rmse_mae_ts}
\end{figure}

\begin{figure}
  \centering
  \begin{subfigure}{.32\textwidth}
  	\includegraphics{plots/simulation_same_rmse_mae/4q_plot_1}
  \end{subfigure}
  \begin{subfigure}{.32\textwidth}
  	\includegraphics{plots/simulation_same_rmse_mae/4q_plot_2}
  \end{subfigure}
    \begin{subfigure}{.32\textwidth}
  	\includegraphics{plots/simulation_same_rmse_mae/4q_plot_3}
  \end{subfigure}
  \caption{4Q-Plot for Simulation~\ref{sec:simulation_rmse_mae} with $T = 100$, $\sigma_y=0.1$, $a = 10$, $p_2 = 0.8$, and $p_3 = (0.9, 0.5)$.}
  \label{fig:simulation_rmse_mae_4q}
\end{figure}
